---
title: "Relationship between article impact and centralities of authors"
author: "Aaron Plex"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Uploading data

```{r, message=FALSE, warning=FALSE}
library(igraph)
library(readxl)
library(viridis)
library(dplyr)

author.list<- read_excel("Dataset_INA_V18_Sept_2021.xlsx", sheet = "Authors_list")
colnames(author.list)<-c("JournalArticleID","Name","Organization","Country","PredictedGender","GenderAccuracy")
author.list<-as.data.frame(author.list)

journal.list<- read_excel("Dataset_INA_V18_Sept_2021.xlsx", sheet = "JA_list")
clean.ja.list<-journal.list[,c(1,2,3,10,15,16,17,18,19)]
colnames(clean.ja.list)<-c("JournalArticleID","Year","Crop","JournalTitle","ResearchArea","ResearchCountry","Commodity","FlagShipName","FlagshipAcronym")
clean.ja.list<-as.data.frame(clean.ja.list)

# Isolating articles for GLDC
GLDC<-as_tibble(journal.list)%>%
  filter(CRP=="GLDC")
gldc<-author.list[c(6941:10933),]

# Isolating articles for RTB
RTB<-as_tibble(journal.list)%>%
  filter(CRP=="RTB")
rtb<-author.list[c(1:6941),]

```


# Generating a graph object for entire GLDC

```{r, message=FALSE, warning=FALSE, fig.height=4, fig.width=4, dpi=200}
#GLDC

matGLDC<-matrix(0,nrow=length(unique(gldc$Name)),ncol=length(unique(gldc$Name))) #adjacency matrix of zeros for authors
colnames(matGLDC)<-unique(gldc$Name)
rownames(matGLDC)<-unique(gldc$Name)
dim(matGLDC)

ja.GLDC<-clean.ja.list
ja.GLDC<-(ja.GLDC[which(ja.GLDC$JournalArticleID>=722),]) #721 is the last row of RTB articles

dim(ja.GLDC) 

for(k in ja.GLDC$JournalArticleID){
  vec=gldc$Name[which(gldc$JournalArticleID==k)]
  for(i in 1:length(vec)){
    for(j in 1:length(vec)){
      matGLDC[which(rownames(matGLDC)==vec[i]),which(rownames(matGLDC)==vec[j])]<-1 #if two scientists co-authored, put a 1 in the adjacency matrix
    }
  }
}

diag(matGLDC)<-0

for(i in 1:dim(matGLDC)[1]){
  for(j in 1:dim(matGLDC)[1]){
    if(matGLDC[i,j]>=1){
      matGLDC[j,i]<-0 #remove loops
    }
  }
}

netGLDC<-graph_from_adjacency_matrix(matGLDC)
```

## Estimating network metrics by authors: GLDC
```{r, message=FALSE, warning=FALSE, fig.height=4, fig.width=4, dpi=200}
# Node degree
degreeGLDC <- as.matrix(degree(netGLDC, mode="total"))

# Node betweenness
betweennessGLDC<-as.matrix(betweenness(netGLDC, v=V(netGLDC), directed = FALSE))

# Eigenvector centrality
eigenGLDC<-eigen_centrality(netGLDC, directed = FALSE)
eigenGLDC<-as.matrix(eigenGLDC$vector)

# PageRank centrality
pageRankGLDC<-page_rank(netGLDC, vids = V(netGLDC), directed = FALSE)
pageRankGLDC<-as.matrix(pageRankGLDC$vector)

authorGLDC<-rownames(pageRankGLDC)

GLDCcentralities<-as_tibble(cbind(authorGLDC, degreeGLDC, betweennessGLDC, eigenGLDC, pageRankGLDC))%>%
  rename(author=authorGLDC,
         degree=V2,
         betweenness=V3,
         eigenvector=V4,
         pageRank=V5)
```


# Generating a graph object for entire RTB

```{r, message=FALSE, warning=FALSE, fig.height=4, fig.width=4, dpi=200}
#RTB

matRTB<-matrix(0,nrow=length(unique(rtb$Name)),ncol=length(unique(rtb$Name))) #adjacency matrix of zeros for authors
colnames(matRTB)<-unique(rtb$Name)
rownames(matRTB)<-unique(rtb$Name)
dim(matRTB)

ja.RTB<-clean.ja.list 
ja.RTB<-(ja.RTB[which(ja.RTB$JournalArticleID<722),]) #721 is the last row of RTB articles

dim(ja.RTB) #715x9

for(k in ja.RTB$JournalArticleID){
  vec=rtb$Name[which(rtb$JournalArticleID==k)]
  for(i in 1:length(vec)){
    for(j in 1:length(vec)){
      matRTB[which(rownames(matRTB)==vec[i]),which(rownames(matRTB)==vec[j])]<-1 #if two scientists coauthored, put a 1 in the adjacency matrix
    }
  }
}

diag(matRTB)<-0

for(i in 1:dim(matRTB)[1]){
  for(j in 1:dim(matRTB)[1]){
    if(matRTB[i,j]>=1){
      matRTB[j,i]<-0 #remove loops
    }
  }
}

netRTB<-graph_from_adjacency_matrix(matRTB)

```

## Estimating network metrics by authors: RTB
```{r, message=FALSE, warning=FALSE, fig.height=4, fig.width=4, dpi=200}
# Node degree
degreeRTB <- as.matrix(degree(netRTB, mode="total"))

# Node betweenness
betweennessRTB<-as.matrix(betweenness(netRTB, v=V(netRTB), directed = FALSE))

# Eigenvector centrality
eigenRTB<-eigen_centrality(netRTB, directed = FALSE)
eigenRTB<-as.matrix(eigenRTB$vector)

# PageRank centrality
pageRankRTB<-page_rank(netRTB, vids = V(netRTB), directed = FALSE)
pageRankRTB<-as.matrix(pageRankRTB$vector)

# Joining centralities
authorRTB<-rownames(pageRankRTB)

RTBcentralities<-as_tibble(cbind(authorRTB, degreeRTB, betweennessRTB, eigenRTB, pageRankRTB))%>%
  rename(author=authorRTB,
         degree=V2,
         betweenness=V3,
         eigenvector=V4,
         pageRank=V5)
```


## Estimating network metrics by article:
```{r, message=FALSE, warning=FALSE, fig.height=4, fig.width=4, dpi=200}
# RTB
authorRTB<-author.list[,c(1,2)]%>%
  rename(author=Name)%>%
  filter(JournalArticleID<722)%>%
  group_by(JournalArticleID, author)%>%
  summarise(count=1)

author_netricRTB<-merge(authorRTB, RTBcentralities, by="author")%>%
  arrange(JournalArticleID)
article_netricRTB<-author_netricRTB%>%
  group_by(JournalArticleID)%>%
  summarise(team_size=sum(as.numeric(count)),
            degreeArt=sum(as.numeric(degree)),
            betweennessArt=sum(as.numeric(betweenness)),
            eigenvectorArt=sum(as.numeric(eigenvector)),
            pageRankArt=sum(as.numeric(pageRank)))

# GLDC
authorGLDC<-author.list[,c(1,2)]%>%
  rename(author=Name)%>%
  filter(JournalArticleID>721)%>%
  group_by(JournalArticleID, author)%>%
  summarise(count=1)

author_netricGLDC<-merge(authorGLDC, GLDCcentralities, by="author")%>%
  arrange(JournalArticleID)
article_netricGLDC<-author_netricGLDC%>%
  group_by(JournalArticleID)%>%
  summarise(team_size=sum(as.numeric(count)),
            degreeArt=sum(as.numeric(degree)),
            betweennessArt=sum(as.numeric(betweenness)),
            eigenvectorArt=sum(as.numeric(eigenvector)),
            pageRankArt=sum(as.numeric(pageRank)))

## Merging data of RTB and GLDC
article_metric<-rbind(article_netricRTB, article_netricGLDC)

## Data on Web of Science citations
WOScitations <- read_excel("Dataset_INA_V19_Only_Citations.xlsx",sheet = "JA_list_citations")
#WOScitations<-

## Data on Altmetric score
altmetric_score <- read_excel("Dataset_INA_V20_Only_Altmetric.xlsx",sheet = "JA_list_Altmetric")

## Data on citations
citation_metric<-merge(WOScitations[,c(1,2,3,10)], 
                       altmetric_score[,c(1,3)],
                       by="UID_JA")%>%
  rename(JournalArticleID="UID_JA",
         WoScitation="Times_Cited_Only_WoS_Core_Collection",
         altmetric="Altmetric_Attention_Score")

## Data on article centrality and citations
citation_centrality<-merge(article_metric,
                           citation_metric,
                           by="JournalArticleID")

## Missing values
citation_centrality[citation_centrality=="NA"]<-c("")
citation_centrality[citation_centrality=="Na"]<-c("")

## Standardizing ciatations metrics by year
citation_centrality<-citation_centrality%>%
  mutate(WoScitation=as.numeric(WoScitation),
         altmetric=as.numeric(altmetric))%>%
  group_by(AR_Year)%>%
  mutate(norm_WoS=WoScitation/mean(WoScitation, na.rm=TRUE),
         norm_altmetric=altmetric/mean(altmetric, na.rm=TRUE))
```


## Article degree and citations
```{r, message=FALSE, warning=FALSE, fig.height=4, fig.width=4, dpi=200}
library(ggplot2)

ggplot(data = citation_centrality, 
       aes(x=degreeArt, y=as.numeric(WoScitation)))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_x_log10()+
  scale_y_log10()+
  labs(x="Article degree by authors",
       y="WoS citations",
       color="Publication year")+
  theme_bw()

ggplot(data = citation_centrality, 
       aes(x=degreeArt/team_size, y=as.numeric(WoScitation)/team_size))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Mean article degree by authors",
       y="Mean WoS citations",
       color="Publication year")+
  theme_bw()

ggplot(data = citation_centrality, 
       aes(x=degreeArt, y=as.numeric(altmetric)))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_x_log10()+
  scale_y_log10()+
  labs(x="Article degree by authors",
       y="Altmetric score",
       color="Publication year")+
  theme_bw()

ggplot(data = citation_centrality, 
       aes(x=degreeArt/team_size, y=as.numeric(altmetric)/team_size))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Mean article degree by authors",
       y="Mean altmetric score",
       color="Publication year")+
  theme_bw()
```

## Article betweenness and citations
```{r, message=FALSE, warning=FALSE, fig.height=4, fig.width=4, dpi=200}
ggplot(data = citation_centrality, 
       aes(x=betweennessArt, y=as.numeric(WoScitation)))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Article betweenness by authors",
       y="WoS citations",
       color="Publication year")+
  theme_bw()

ggplot(data = citation_centrality, 
       aes(x=betweennessArt/team_size, y=as.numeric(WoScitation)/team_size))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Mean article betweenness by authors",
       y="Mean WoS citations",
       color="Publication year")+
  theme_bw()

ggplot(data = citation_centrality, 
       aes(x=betweennessArt, y=as.numeric(altmetric)))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Article betweenness by authors",
       y="Altmetric score",
       color="Publication year")+
  theme_bw()

ggplot(data = citation_centrality, 
       aes(x=betweennessArt/team_size, y=as.numeric(altmetric)/team_size))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Mean article betweenness by authors",
       y="Mean altmetric score",
       color="Publication year")+
  theme_bw()
```


## Article eigenvector centrality and citations
```{r, message=FALSE, warning=FALSE, fig.height=4, fig.width=4, dpi=200}
ggplot(data = citation_centrality, 
       aes(x=eigenvectorArt, y=as.numeric(WoScitation)))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_x_log10()+
  scale_y_log10()+
  labs(x="Article eigenvector by authors",
       y="WoS citations",
       color="Publication year")+
  theme_bw()

ggplot(data = citation_centrality, 
       aes(x=eigenvectorArt/team_size, y=as.numeric(WoScitation)/team_size))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Mean article eigenvector by authors",
       y="Mean WoS citations",
       color="Publication year")+
  theme_bw()

ggplot(data = citation_centrality, 
       aes(x=eigenvectorArt/team_size, y=as.numeric(altmetric)/team_size))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Mean article eigenvector by authors",
       y="Mean altmetric score",
       color="Publication year")+
  theme_bw()

ggplot(data = citation_centrality, 
       aes(x=eigenvectorArt/team_size, y=as.numeric(altmetric)/team_size))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth(aes(fill=CRP), method = "lm")+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Mean article eigenvector by authors",
       y="Mean altmetric score",
       color="Publication year")+
  theme_bw()
```


## Article PageRank centrality and citations
```{r, message=FALSE, warning=FALSE, fig.height=4, fig.width=4, dpi=200}
ggplot(data = citation_centrality, 
       aes(x=pageRankArt/team_size, y=as.numeric(WoScitation)/team_size))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Mean article PageRank by authors",
       y="Mean WoS citations",
       color="Publication year")+
  theme_bw()


ggplot(data = citation_centrality, 
       aes(x=pageRankArt/team_size, y=as.numeric(altmetric)/team_size))+
  geom_point(aes(color=as.character(AR_Year), alpha=0.1), show.legend = FALSE)+
  geom_smooth()+
  scale_color_viridis(discrete = TRUE)+
  scale_y_log10()+
  labs(x="Mean article PageRank by authors",
       y="Mean altmetric score",
       color="Publication year")+
  theme_bw()
```


```{r}
library(GGally)

## Dataset with unscaled centralities and citations
ggcorr(citation_centrality[,c(2:6,9,10)])
## Dataset with unscaled centralities and normalized citations
ggcorr(citation_centrality[,c(2:6,11,12)])
```

```{r}
scaled_centrality<-citation_centrality[,c(2:6,11,12)]%>%
  mutate(degreeArt=degreeArt/team_size,
         betweennessArt=betweennessArt/team_size,
         eigenvectorArt=eigenvectorArt/team_size,
         pageRankArt=pageRankArt/team_size,
         norm_WoS=log10((norm_WoS+1)/team_size),
         norm_altmetric=log10((norm_altmetric+1)/team_size))

colnames(scaled_centrality)<-c("Authors","Degree","Betweenness","Eigenvector","PageRank","WoS","Altmetric")
```


```{r}
## Dataset with scaled centralities and normalized citations
ggcorr(scaled_centrality,
       label = TRUE,
       label_color = "white",
       label_alpha = FALSE)+
  scale_fill_viridis(discrete = FALSE)+
  labs(fill="Pearson \ncoefficient")
```

