---
title: "General organization networks"
author: "Aaron Plex"
date: "`r format(Sys.time(), '%d %B, %Y')`"

output:
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    number_sections: TRUE
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Network of institutions GLDC

```{r, message=FALSE, warning=FALSE}
library(igraph)
library(readxl)
library(viridis)
library(tidyverse)

author.list<- read_excel("Dataset_INA_V18_Sept_2021.xlsx", sheet = "Authors_list")
colnames(author.list)<-c("JournalArticleID","Name","Organization","Country","PredictedGender","GenderAccuracy")
author.list<-as.data.frame(author.list)

journal.list<- read_excel("Dataset_INA_V18_Sept_2021.xlsx", sheet = "JA_list")
clean.ja.list<-journal.list[,c(1,2,3,10,15,16,17,18,19)]
colnames(clean.ja.list)<-c("JournalArticleID","Year","Crop","JournalTitle","ResearchArea","ResearchCountry","Commodity","FlagShipName","FlagshipAcronym")
clean.ja.list<-as.data.frame(clean.ja.list)

# Isolating articles for GLDC
GLDC<-as_tibble(journal.list)%>%
  filter(CRP=="GLDC")
gldc<-author.list[c(6941:10933),]

# Isolating articles for RTB
RTB<-as_tibble(journal.list)%>%
  filter(CRP=="RTB")
rtb<-author.list[c(1:6941),]

```


# Generating a graph object for entire GLDC

```{r}
#GLDC

matGLDC<-matrix(0,nrow=length(unique(gldc$Organization)),ncol=length(unique(gldc$Organization))) #adjacency matrix of zeros for institutions
colnames(matGLDC)<-unique(gldc$Organization)
rownames(matGLDC)<-unique(gldc$Organization)
dim(matGLDC)

ja.GLDC<-clean.ja.list
ja.GLDC<-(ja.GLDC[which(ja.GLDC$JournalArticleID>=722),]) #721 is the last row of RTB articles

dim(ja.GLDC)

for(k in ja.GLDC$JournalArticleID){
  vec=gldc$Organization[which(gldc$JournalArticleID==k)]
  for(i in 1:length(vec)){
    for(j in 1:length(vec)){
      matGLDC[which(rownames(matGLDC)==vec[i]),which(rownames(matGLDC)==vec[j])]<-1 #if two organizations collaborate, put a 1 in the adjacency matrix
    }
  }
}

diag(matGLDC)<-0

for(i in 1:dim(matGLDC)[1]){
  for(j in 1:dim(matGLDC)[1]){
    if(matGLDC[i,j]>=1){
      matGLDC[j,i]<-0 #remove loops
    }
  }
}

netGLDC<-graph_from_adjacency_matrix(matGLDC)
degGLDC <- degree(netGLDC, mode="total")

#hist(degGLDC)

V(netGLDC)$Organization<-rownames(matGLDC)
```


## Identifying collaboration with CGIAR centers for GLDC
```{r}
edgelist_GLDC<-as_tibble(get.edgelist(netGLDC)) %>%
   mutate(region1 = ifelse(V1 == "Alliance Biovers Int & CIAT", 1, 0),
         region2 = ifelse(V1 == "Biovers Int", 1, 0),
         region3 = ifelse(V1 == "CIAT", 1, 0),
         region4 = ifelse(V1 == "ICARDA", 1, 0),
         region5 = ifelse(V1 == "ICRAF", 1, 0),
         region6 = ifelse(V1 == "ICRISAT", 1, 0),
         region7 = ifelse(V1 == "IITA", 1, 0),
         region8 = ifelse(V1 == "ILRI", 1, 0),
         region9 = ifelse(V1 == "CIRAD", 1, 0),
         region10 = ifelse(V1 == "CSIRO", 1, 0),
         region11 = ifelse(V1 == "IRD", 1, 0),
         region12 = ifelse(V2 == "Alliance Biovers Int & CIAT", 1, 0),
         region13 = ifelse(V2 == "Biovers Int", 1, 0),
         region14 = ifelse(V2 == "CIAT", 1, 0),
         region15 = ifelse(V2 == "ICARDA", 1, 0),
         region16 = ifelse(V2 == "ICRAF", 1, 0),
         region17 = ifelse(V2 == "ICRISAT", 1, 0),
         region18 = ifelse(V2 == "IITA", 1, 0),
         region19 = ifelse(V2 == "ILRI", 1, 0),
         region20 = ifelse(V2 == "CIRAD", 1, 0),
         region21 = ifelse(V2 == "CSIRO", 1, 0),
         region22 = ifelse(V2 == "IRD", 1, 0),
         region = region1+region2+region3+region4+region5+region6+region7+region8+region9+region10+region11+region12+region13+region14+region15+region16+region17+region18+region19+region20+region21+region22,
         Region = ifelse(region >= 1, "CG center", "Other center")) %>%
  dplyr::select(V1, V2, Region)

nodelist_GLDC<-data.frame(unique(c(edgelist_GLDC$V1, edgelist_GLDC$V2))) 
colnames(nodelist_GLDC)<-c("V1")


nodelist_GLDC<-nodelist_GLDC%>%
  mutate(region1 = ifelse(V1 == "Alliance Biovers Int & CIAT", 1, 0),
         region2 = ifelse(V1 == "Biovers Int", 1, 0),
         region3 = ifelse(V1 == "CIAT", 1, 0),
         region4 = ifelse(V1 == "ICARDA", 1, 0),
         region5 = ifelse(V1 == "ICRAF", 1, 0),
         region6 = ifelse(V1 == "ICRISAT", 1, 0),
         region7 = ifelse(V1 == "IITA", 1, 0),
         region8 = ifelse(V1 == "ILRI", 1, 0),
         region9 = ifelse(V1 == "CIRAD", 1, 0),
         region10 = ifelse(V1 == "CSIRO", 1, 0),
         region11 = ifelse(V1 == "IRD", 1, 0),
         region = region1+region2+region3+region4+region5+region6+region7+region8+region9+region10+region11,
         Region = ifelse(region >= 1, "CG center", "Other center")) %>%
  dplyr::select(V1, Region)%>%
  rename(Center_abbreviation=V1)

# Institutions categories
partner_listGLDC<-read_excel("Partners_list_GLDC_RTB.xlsx", sheet = "GLDC - Partners")

nodelist_GLDC<-merge(nodelist_GLDC, partner_listGLDC, by="Center_abbreviation", all.x = TRUE)%>%
  replace_na(list(Status="Collaborator"))

new_GLDC<-graph_from_data_frame(d=edgelist_GLDC,
                                vertices = nodelist_GLDC,
                                directed = FALSE)

new_deg<-degree(new_GLDC)
new_betweenness<-betweenness(new_GLDC, v = V(new_GLDC))
```



# Network of institutional collaborations in the GLDC research program

```{r, fig.width=12, fig.height=15, dpi=300}
library(ggraph)
library(dplyr)

betweenness_GLDC <- igraph::betweenness(netGLDC, v = V(netGLDC), directed = FALSE, weights = E(netGLDC)$weight)

organization_GLDC<-ggraph(netGLDC, "stress",bbox = 5)+
  geom_edge_link(edge_width=0.1, colour="grey66")+
  geom_node_point(aes(fill = degGLDC,
                      colour = degGLDC,
                      size = betweenness_GLDC), 
                  shape = 21, show.legend = FALSE)+
  scale_edge_width_continuous(range = c(0.005,0.5))+
  scale_size_continuous(range = c(3,10))+
  scale_fill_viridis_c(name="Degree", option = "viridis", direction = -1, begin = 0.3, end = 0.9)+
  scale_color_viridis_c(option = "viridis", direction = -1, begin = 0.3, end = 0.9)+
  geom_node_text(aes(label = ifelse(degGLDC>75,rownames(as.matrix(degGLDC)),NA)), size=5, repel = TRUE)+
  
  theme(legend.colour = element_blank())+
  theme_void()
  
organization_GLDC + 
  ggtitle("GLDC") +
  theme(plot.title = element_text(colour = "#000066",
                                  size = 20,
                                  face = "bold.italic",
                                  hjust = c(0.5)))
```



```{r, , fig.width=10, fig.height=13, dpi=400}
institution_GLDC<-ggraph(new_GLDC, "stress",bbox = 5)+
  geom_edge_link(aes(colour=edgelist_GLDC$Region), edge_width=0.2)+
  geom_node_point(aes(fill = new_deg,
                      colour = new_deg,
                      size = new_betweenness, 
                      shape = Status),
                  show.legend = TRUE)+
  scale_shape_manual(values = c("Collaborator"=19,"Program participant"=17,"Planning partner"=15))+
  scale_edge_color_viridis(discrete = TRUE, option = "rocket", begin = 0.4, end = 0.9)+
  scale_edge_width_continuous(range = c(0.005,0.5))+
  scale_size_continuous(range = c(3,10))+
  scale_fill_viridis_c(name="Degree", option = "viridis", direction = -1, begin = 0.3, end = 0.9)+
  scale_color_viridis_c(option = "viridis", direction = -1, begin = 0.3, end = 0.9)+
  geom_node_text(aes(label = ifelse(new_deg>75,rownames(as.matrix(new_deg)),NA)), size=4, repel = TRUE)+
  theme(legend.colour = element_blank())+
  theme_void()
  
institution_GLDC + 
  ggtitle("GLDC") +
  theme(plot.title = element_text(colour = "#000066",
                                  size = 20,
                                  face = "bold.italic",
                                  hjust = c(0.5)))+
  guides(fill=guide_legend(title = "Node degree"),
         color=guide_legend(title = "Node degree",
                           override.aes = list(size=7)),
         size=guide_legend(title = "Betweenness"),
         shape=guide_legend(title = "Institution type",
                           override.aes = list(size=5)),
          edge_color=guide_legend(title = "Center type",
                           override.aes = list(size=3)))

```


# Generating a graph object for entire RTB

```{r}
#RTB

matRTB<-matrix(0,nrow=length(unique(rtb$Organization)),ncol=length(unique(rtb$Organization))) #adjacency matrix of zeros for institutions
colnames(matRTB)<-unique(rtb$Organization)
rownames(matRTB)<-unique(rtb$Organization)
dim(matRTB)

ja.RTB<-clean.ja.list 
ja.RTB<-(ja.RTB[which(ja.RTB$JournalArticleID<722),]) 

dim(ja.RTB)

for(k in ja.RTB$JournalArticleID){
  vec=rtb$Organization[which(rtb$JournalArticleID==k)]
  for(i in 1:length(vec)){
    for(j in 1:length(vec)){
      matRTB[which(rownames(matRTB)==vec[i]),which(rownames(matRTB)==vec[j])]<-1 #if two organizations collaborate, put a 1 in the adjacency matrix
    }
  }
}

diag(matRTB)<-0

for(i in 1:dim(matRTB)[1]){
  for(j in 1:dim(matRTB)[1]){
    if(matRTB[i,j]>=1){
      matRTB[j,i]<-0 #remove loops
    }
  }
}

netRTB<-graph_from_adjacency_matrix(matRTB)
degRTB <- degree(netRTB, mode="total")

#hist(degRTB)

V(netRTB)$Organization<-rownames(matRTB)
```


## Identifying collaboration with CGIAR centers for RTB
```{r}
edgelist_RTB<-as_tibble(get.edgelist(netRTB)) %>%
   mutate(region1 = ifelse(V1 == "Alliance Biovers Int & CIAT", 1, 0),
         region2 = ifelse(V1 == "Biovers Int", 1, 0),
         region3 = ifelse(V1 == "CIAT", 1, 0),
         region4 = ifelse(V1 == "CIP", 1, 0),
         region5 = ifelse(V1 == "IITA", 1, 0),
         region6 = ifelse(V1 == "CIRAD", 1, 0),
         region7 = ifelse(V2 == "Alliance Biovers Int & CIAT", 1, 0),
         region8 = ifelse(V2 == "Biovers Int", 1, 0),
         region9 = ifelse(V2 == "CIAT", 1, 0),
         region10 = ifelse(V2 == "CIP", 1, 0),
         region11 = ifelse(V2 == "IITA", 1, 0),
         region12 = ifelse(V2 == "CIRAD", 1, 0),
         region = region1+region2+region3+region4+region5+region6+region7+region8+region9+region10+region11+region12,
         Region = ifelse(region >= 1, "CG center", "Other center")) %>%
  dplyr::select(V1, V2, Region)

nodelist_RTB<-data.frame(unique(c(edgelist_RTB$V1, edgelist_RTB$V2))) 
colnames(nodelist_RTB)<-c("V1")


nodelist_RTB<-nodelist_RTB%>%
  mutate(region1 = ifelse(V1 == "Alliance Biovers Int & CIAT", 1, 0),
         region2 = ifelse(V1 == "Biovers Int", 1, 0),
         region3 = ifelse(V1 == "CIAT", 1, 0),
         region4 = ifelse(V1 == "CIP", 1, 0),
         region5 = ifelse(V1 == "IITA", 1, 0),
         region6 = ifelse(V1 == "CIRAD", 1, 0),
         region = region1+region2+region3+region4+region5+region6,
         Region = ifelse(region >= 1, "CG center", "Other center")) %>%
  dplyr::select(V1, Region)%>%
  rename(Center_abbreviation=V1)

# Institutions categories
partner_listRTB<-read_excel("Partners_list_GLDC_RTB.xlsx", sheet = "RTB - Partners")
nodelist_RTB<-merge(nodelist_RTB, partner_listRTB, by="Center_abbreviation", all.x = TRUE)%>%
  replace_na(list(Status="Collaborator"))


new_RTB<-graph_from_data_frame(d=edgelist_RTB,
                                vertices = nodelist_RTB,
                                directed = FALSE)

new_degRTB<-degree(new_RTB)
new_betweennessRTB<-betweenness(new_RTB, v = V(new_RTB))
```


# Network of institutional collaborations in RTB research programs

```{r, fig.width=12, fig.height=15, dpi=300}

betweenness_RTB <- igraph::betweenness(netRTB, v = V(netRTB), directed = FALSE, weights = E(netRTB)$weight)

organization_RTB<-ggraph(netRTB, "stress",bbox = 5)+
  geom_edge_link(edge_width=0.1, colour="grey66")+
  geom_node_point(aes(fill = degRTB,
                      colour = degRTB,
                      size = betweenness_RTB), 
                  shape = 21, show.legend = FALSE)+
  scale_edge_width_continuous(range = c(0.005,0.5))+
  scale_size_continuous(range = c(3,10))+
  scale_fill_viridis_c(name="Degree", option = "viridis", direction = -1, begin = 0.3, end = 0.9)+
  scale_color_viridis_c(option = "viridis", direction = -1, begin = 0.3, end = 0.9)+
  geom_node_text(aes(label = ifelse(degRTB>75,rownames(as.matrix(degRTB)),NA)), size=5, repel = TRUE)+
  
  theme(legend.colour = element_blank())+
  theme_void()

organization_RTB + 
  ggtitle("RTB") +
  theme(plot.title = element_text(colour = "#000066",
                                  size = 20,
                                  face = "bold.italic",
                                  hjust = c(0.5)))
```


```{r, , fig.width=12, fig.height=15, dpi=400}
institution_RTB<-ggraph(new_RTB, "stress",bbox = 5)+
  geom_edge_link(aes(color=edgelist_RTB$Region), edge_width=0.2)+
  geom_node_point(aes(fill = new_degRTB,
                      colour = new_degRTB,
                      size = new_betweennessRTB, 
                      shape = Status),
                  show.legend = TRUE)+
  scale_shape_manual(values = c("Collaborator"=19,"Program participant"=17,"Planning partner"=15))+
  scale_edge_color_viridis(discrete = TRUE, option = "rocket", begin = 0.4, end = 0.9)+
  scale_edge_width_continuous(range = c(0.005,0.5))+
  scale_size_continuous(range = c(3,10))+
  scale_fill_viridis_c(name="Degree", option = "viridis", direction = -1, begin = 0.3, end = 0.9)+
  scale_color_viridis_c(option = "viridis", direction = -1, begin = 0.3, end = 0.9)+
  geom_node_text(aes(label = ifelse(new_degRTB>75,rownames(as.matrix(new_degRTB)),NA)), size=5, repel = TRUE)+
  
  theme(legend.colour = element_blank())+
  theme_void()
  
institution_RTB + 
  ggtitle("RTB") +
  theme(plot.title = element_text(colour = "#000066",
                                  size = 20,
                                  face = "bold.italic",
                                  hjust = c(0.5)))+
  guides(fill=guide_legend(title = "Node degree"),
         color=guide_legend(title = "Node degree",
                           override.aes = list(size=7)),
         size=guide_legend(title = "Betweenness"),
         shape=guide_legend(title = "Institution type",
                           override.aes = list(size=5)),
         edge_color=guide_legend(title = "Center type",
                           override.aes = list(size=3)))

```


```{r, fig.height=5,fig.width=5}
teams<-author.list%>%
#  filter(JournalArticleID>721)%>%
  group_by(JournalArticleID)%>%
  summarise(team_size=length(Name))
team_distribution<-teams%>%
  group_by(team_size)%>%
  summarise(count=length(JournalArticleID))%>%
  mutate(density=count/sum(count))
total=sum(team_distribution$count)

ggplot(data = team_distribution,aes(x=team_size,y=count/total))+
  geom_smooth(color="red")+
  geom_vline(xintercept=mean(teams$team_size),size=1)+
  geom_point()+
  scale_x_log10()+
  scale_y_log10()+
  theme()
mean(teams$team_size)
```


```{r}
CGRTB_collaboration<-edgelist_RTB%>%
  group_by(Region)%>%
  summarise(count=length(Region))%>%
  mutate(proportion=count/sum(count))
CGRTB_collaboration

CGGLDC_collaboration<-edgelist_GLDC%>%
  group_by(Region)%>%
  summarise(count=length(Region))%>%
  mutate(proportion=count/sum(count))
CGGLDC_collaboration
```



Most articles included scientific teams of 6 researchers, and mean team size is 9.88 (~10) researchers.
